Humanized Quadcopter Swarm System for IARC 2019

### 2019-06-01 IARC_Paper_2019/Paper.tex
Submitted.

The eCalc online tool was used to validate our calculations, and as seen by the graph on the following page, there should be no issue reaching flight times over 8 minutes at speeds below 15 [mph].

@@

			We have made slight modifications to the ArduCopter firmware, which allow us to set the EKF origin from our GNC ROS node. This has been done to make our drones capable of navigating in GPS denied environments. For general waypoint navigation, the drones utilize the ArduCopter EKF that takes in data from the sensors listed above, including the optical flow, compass, and IMU. The EKF position is then queried via mavros so that our navigation code can use our position to make intelligent decisions. TAR has greatly improved ArduCopter’s GPS denied capabilities by integrating ORBSLAM into the ArduCopter EKF. The use of ORBSLAM allows the drone to navigate based on 3 dimensional visual features in the drones operating environment. ORBSLAM continuously builds a map of its environment and compares current local maps to its master. Because of this comparison algorithm, ORBSLAM is able to perform loop closure which is useful in negating any propagated error from the rate sensors.

@@

			A crucial aspect of navigating in a GPS-denied is concrete information on our position. Using a Teraranger One Time of Flight sensor from Terabee, our drones are able to know their exact altitude. This sensor was chosen due to its extremely light weight over other LiDAR options. This communicates over I2C directly to the Pixhawk where ArduCopter uses that information in the EKF.

>>>>

The eCalc online tool was used to validate our calculations, and as seen by the graph on the following page, there should be no issue reaching flight times of 8 minutes at speeds below 15 [mph].

@@

			We have made slight modifications to the ArduCopter firmware, which allow us to set the EKF origin from our GNC ROS node. This has been done to make our drones capable of navigating in GPS denied environments. For general waypoint navigation, the drones utilize the ArduCopter EKF that takes in data from the sensors listed above, including the optical flow, compass, and IMU. The EKF position is then queried via mavros so that our navigation code can use our position to make intelligent decisions. TAR has greatly improved ArduCopter’s GPS denied capabilities by integrating ORBSLAM into the ArduCopter EKF. The use of ORBSLAM allows the drone to navigate based on 3 dimensional visual features in the drones operating environment. ORBSLAM continuously builds a map of its environment and compares current local maps to its master. Because of this comparison algorithm, ORBSLAM is able to perform loop closure, which is useful in negating any propagated error from the rate sensors.

@@

			A crucial aspect of navigating in a GPS-denied area is concrete information on our position. Using a Teraranger One Time of Flight sensor from Terabee, our drones are able to know their exact altitude. This sensor was chosen due to its extremely light weight over other LiDAR options. This communicates over I2C directly to the Pixhawk where ArduCopter uses that information in the EKF.
